# **Data availability status report**
## `r as.character(format(Sys.Date(), format="%B %d, %Y"))`
========================================================

```{r, include=FALSE}
library(knitr)
app <- read.delim(file.path("../..", "inputs", "appendix-b.tsv"), 
									colClasses = "character")

app <- 
  subset(app, select = c("Figure.Number", "Title", "Page", "Data.Availability"))

# set up data frames for found and not found data
app_found <- 
  subset(app, grepl("Read off|Online|R data set|Splus", app$Data.Availability))

app_notfound <- 
  subset(app, grepl("Estimate|Not found|Random", app$Data.Availability))
    
read <- sum(grepl("Read off", app$Data.Availability))
dataset <- sum(grepl("data set", app$Data.Availability))
online <- sum(grepl("Online", app$Data.Availability))
est <- sum(grepl("Estimate", app$Data.Availability))
nfound <- sum(grepl("Not found", app$Data.Availability))
rand_no <- sum(grepl("Random", app$Data.Availability))
tot <- sum(dataset + est + nfound + online + rand_no + read)

```

### There are a total of `r nrow(app)` figures.  

#### _Data found_ for `r  sum(read + dataset + online)` figures

```{r found_data_table, echo=FALSE, results="asis"}

df_found <- data.frame(
  grp = c("Read off figure or figure description", "Online source", 
          "R or S-Plus data set", "Total"),
  count = c(read, online, dataset, sum(read, dataset, online))
  )

names(df_found) <- c("Data Found", "Number of Figures")

kable(df_found)

```

#### _Data not found_ for `r  sum(est + nfound + rand_no)` figures

```{r not found data table, echo=FALSE, results="asis"}

df_notfound <- data.frame(
  grp = c("Not found", "Estimate from figure", "Random numbers", "Total"),
  count = c(nfound, est, rand_no, sum(nfound, est, rand_no))
  )

names(df_notfound) <- c("Data not Found", "Number of Figures")

kable(df_notfound)

```

The following consists of the breakdown of each group of figures with no data found.

#### Data sets that couldn't be found and are difficult to estimate are as follows:

```{r no_data_table, echo=FALSE, results="asis"}

library(plyr) #ddply() , join_all() , count()

# get all not found datasets
t <- subset(app_notfound, grepl("Not found", Data.Availability),
						select = -Title)

df1 <- count(t, "Data.Availability")

df2 <- ddply(t, .(Data.Availability), summarise, 
             paste(Figure.Number, collapse = ", "))

df3 <- ddply(t, .(Data.Availability), summarise, paste(Page, collapse = ", "))

df4 <- join_all(list(df1, df2, df3) , "Data.Availability")


# clean up df: shorten names, order by frequency, rename columns
df4$Data.Availability <- gsub("Not found ; | data", "", df4$Data.Availability)
df4 <- data.frame(df4[order(-df4$freq), ], row.names = NULL)

# append "total"" row
df4 <- rbind(df4, c("Total", sum(df1$freq), "", ""))

names(df4) <- c("Data set" , "Number of Figures", "Figure Number(s)", "Page(s)")

kable(df4)

```

#### The data used for the following figures could be estimated from the figure itself.

```{r estimate_table, echo=FALSE, results="asis"}

# get all estimable data sets
df_est <- subset(app_notfound, grepl("Estimate", Data.Availability), 
								 select = -Data.Availability)

# reorder and rename columns
df_est <- data.frame(df_est[, c("Figure.Number", "Title", "Page")], 
										 row.names = NULL)

# append 'total' row
df_est <- rbind(df_est, c("Total", nrow(df_est), "", ""))

names(df_est) <- c("Figure Number", "Name", "Page")

kable(df_est)
```

#### The following figures use data sets generated from random numbers:

```{r random_number_table, echo=FALSE, results="asis"}
df_rand_no <- 
  data.frame(subset(app_notfound, select = c("Figure.Number", "Title", "Page"), 
                    Data.Availability == "Random numbers"), row.names = NULL)

# append 'total' row
df_rand_no <- data.frame(rbind(df_rand_no, c("Total", nrow(df_rand_no), "")))

names(df_rand_no) <- c("Figure Number", "Name", "Page")

kable(df_rand_no)
```


